---
# General Settings
format: html
echo: false
warning: false

# Theme Settings
theme: default
barposition: top
footer-left: "Made with [surveydown](https://surveydown.org)"
footer-right: '[<i class="bi bi-github"></i> Source Code](https://github.com/surveydown-dev/template_default)'

# Survey Settings
use-cookies: false
auto-scroll: false
rate-survey: false
system-language: en
highlight-unanswered: true
highlight-color: blue
capture-metadata: true
all-questions-required: false
---

```{r}
library(surveydown)
```

::: {.sd_page id=welcome}

# DaSEH Follow-up Survey

Thank you for taking the time to participate in this survey. We are collecting data about user experience with our course to learn more about how to improve the data science education experience. This data may ultimately be used for a research publication and reporting to the NIH.

**DATA CONFIDENTIALITY:** This survey is anonymous. The potential risks to you are small. The potential benefits to the community of data scientists, developers, and professors are very high – we will be able to learn how we can improve data science/environmental health education material.

**DATA SHARING:** We plan to release the data collected from this survey only in aggregate form using GitHub (https://github.com/). No personally identifiable information is collected or will be shared.

**PARTICIPATION:** You must be 18 or over to participate. You will be asked a series of questions about your experience following the DaSEH course you previously took. You can stop participating in the survey at any point. You do not need to answer optional questions. 

Depending on how you answer the survey, this will take **~10 minutes** to complete. You will have an opportunity before submission to edit your responses. Any answers that are ultimately submitted (and not removed by the participant) will continue to be used for research.

**RISK:** Risk of participation is minimal. The questions we ask pose minimal security risk to participants as they focus on your personal experience and expectations. While we have taken measures to ensure the security of the survey responses, please be aware that no online system is completely secure. By participating in this survey, you understand and accept the inherent risks associated with transmitting information over the internet.

**CONSENT:** The first questions will ask if you are over 18 and if you consent (or agree) that the data from your responses be used for research purposes.

**QUESTIONS OR PROBLEMS:** If you have questions or problems, email Ava Hoffman at ahoffma2@fredhutch.org or contact us through the anonymous Code of Conduct Reporting Form.

You may also contact the Fred Hutchinson Cancer Center IRB Office if you have questions about your rights as a participant. Contact the IRB if you feel you have not been treated fairly or if you have other concerns.

This study has been deemed exempt by the Fred Hutchinson Cancer Center IRB, specifically Exempt status (Category (2)(ii) Tests, surveys, interviews, or observation (low risk)). Thus, the proposed activity does not qualify as human subjects research as defined by DHHS regulations 45 CFR 46.102, and does not require IRB oversight.

IRB No.: FHIRB0020064  
Date Approved: 3/19/2024  

The IRB contact information is:  
Address: Fred Hutch Cancer Center Institutional Review Office  
1100 Fairview Ave. N. Mail Stop J2-100, Seattle, WA 98109  
Telephone: 206-667-5900  
E-mail: iro@fredhutch.org  

You cannot participate in this survey if you are under 18.

```{r}
sd_question(
  type   = 'mc',
  id     = 'consent',
  label  = "Are you 18 or over?",
  option = c(
    'Yes' = 'yes', 
    'No' = 'no'
)
)
sd_next()
```

:::

::: {.sd_page id=page2}

```{r}
sd_question(
  type   = 'mc',
  id     = 'how_often_before',
  label  = "How often did you use R before DaSEH?",
  option = c(
    'Extensively (daily or near daily)'    = 'extensively',
    'Regularly (weekly or more)' = 'weekly',
    'A few times to occasionally' = 'occasionally',
    'Less than a few times' = 'few',
    'Never used R before' = 'never'
  )
)

sd_question(
  type   = 'mc',
  id     = 'how_often_now',
  label  = "How often do you use R now?",
  option = c(
    'Extensively (daily or near daily)' = 'extensively',
    'Regularly (weekly or more)' = 'weekly',
    'A few times to occasionally' = 'occasionally',
    'Less than a few times' = 'few',
    'Never since DaSEH' = 'never'
  )
)

sd_question(
  type   = 'mc',
  id     = 'codeathon',
  label  = "Did you participate in the code-a-thon event at Fred Hutch?",
  option = c(
    'Yes' = 'yes', 
    'No' = 'no'
  )
)

sd_next()
```

:::

::: {.sd_page id=page3a}

```{r}
sd_question(
  type   = 'mc_multiple',
  id     = 'r_use_cases',
  label  = "What do you use R for? (Select all that apply)",
  option = c(
    'Data analysis and statistics' = 'data_analysis',
    'Data visualization and graphics' = 'visualization',
    'Data cleaning and wrangling' = 'data_cleaning',
    'Machine learning and modeling' = 'ml_modeling',
    'Academic research' = 'academic',
    'Reporting and communication' = 'reporting',
    'Bioinformatics or genomics' = 'bioinformatics',
    'Geospatial analysis' = 'geospatial',
    'Teaching or training others' = 'teaching',
    'Other' = 'other'
  )
)

sd_question(
  type  = 'text',
  id    = 'coding_practices',
  label = "What is the most important coding practice you have adopted since DaSEH?"
)

sd_question(
  type  = 'text',
  id    = 'reproducibility_practices',
  label = "What is the most important reproducibility practice you have adopted since DaSEH?"
)

sd_next()
```

:::

::: {.sd_page id=page3b}

```{r}
sd_question(
  type   = 'mc_multiple',
  id     = 'why_not_using_r',
  label  = "Why aren't you using R? (Select all that apply)",
  option = c(
    'I don\'t have a need for it in my work' = 'no_need',
    'I don\'t feel confident enough yet' = 'not_confident',
    'I prefer other tools or languages' = 'prefer_other',
    'Lack of time to practice' = 'lack_time',
    'Difficult to learn or understand' = 'difficult',
    'Lack of support or resources' = 'lack_support',
    'My workplace/team doesn\'t use R' = 'workplace_culture',
    'I forgot what I learned' = 'forgot',
    'Other' = 'other'
  )
)
sd_next()
```

:::

::: {.sd_page id=page4}

```{r}
sd_question(
  type   = 'mc',
  id     = 'courses_materials',
  label  = "Have you continued learning R through other courses or materials?",
  option = c(
    'Yes' = 'yes',
    'No' = 'no'
  )
)

sd_question(
  type   = 'mc',
  id     = 'recommended',
  label  = "Have you recommended DaSEH materials to others?",
  option = c(
    'Yes' = 'yes',
    'No' = 'no'
  )
)

sd_question(
  type   = 'mc_multiple',
  id     = 'recommended',
  label  = "Have you returned to any DaSEH materials? (select all that apply)",
  option = c(
    'Slides / pdfs' = 'slides',
    'Cheatsheets' = 'cheatsheets',
    'Video recordings' = 'video',
    'None of these' = 'none'
  )
)

sd_next()
```

:::

::: {.sd_page id=page5}

```{r}
sd_question(
  type   = 'mc',
  id     = 'part_of_journey',
  label  = "DaSEH was an important part of my programming journey.",
  option = c(
    "Strongly Disagree" = "strong_disagree",
    "Disagree"          = "disagree",
    "Neutral"           = "neutral",
    "Agree"             = "agree",
    "Strongly Agree"    = "strong_agree"
  )
)

sd_question(
  type  = 'text',
  id    = 'part_of_journey_text',
  label = "(optional) In 1-2 sentences tell us about your response above."
)

sd_question(
  type  = 'text',
  id    = 'impactful_text',
  label = "What was the most impactful thing you learned as part of DaSEH?"
)

sd_next()
```

:::

::: {.sd_page id=end}

## Thank you for taking this survey!

```{r}
sd_close()
```

:::

::: {.sd_page id=screenout}

## Thank you for your interest!

Unfortunately, you do not meet the eligibility requirements for this survey.

:::
